---
output: 
  html_document
title: "Exploratory data analysis"
author: "Matthew Shane Loop, PhD"
---

```{r, include = FALSE}
knitr::opts_chunk$set(message = FALSE, echo=FALSE, fig.width = 10, fig.height = 10, warning=FALSE)
library(Hmisc)
library(tidyverse)
library(GGally)



water <- read_tsv("../data/water_cleaned.txt") %>% mutate_if(is.character, funs(na_if(., ""))) %>%
  mutate(time_pretty = as.character(time_pretty))

water
```

How many unique compounds are there under analysis? `r water %>% distinct(metabolite) %>% nrow()`

How many time points? `r water %>% distinct(time_pretty) %>% nrow()`

* 3 locations as the main unit of analysis (i)
* 11 time points where samples were taken (j)
* 2 extraction methods (k)
* 2 different MS machines (l)
  * but one machine only had 1 extraction method (austin)
* concentrations of 56 different metabolites in each run (m)

Here's a plot of the concentrations of each metabolite vs. time, across the 3 sites.

```{r, fig.width=15, fig.height=10}
water %>%
  ggplot(aes(x = time_pretty, y = value, color = metabolite, linetype = extraction, group = interaction(extraction, metabolite))) +
  geom_path() +
  facet_grid(machine ~location) +
  cowplot::theme_cowplot() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

The shimadzu machine obviously has less variability than the waters machine. The two extractions seem fairly close to one another in most cases, which is reassuring.

## Description and analysis of metabolites
```{r}
water %>%
  select(metabolite, value, location, time_pretty, machine, extraction) %>%
  spread(metabolite, value) %>%
  Hmisc::describe() %>%
  html()
```

These metabolites have both upper and lower limits of detection. Let's look at the distribution of each one, relative to those limits.

```{r}
water %>%
  ggplot(aes(x = value)) +
  geom_histogram(bins = 100) +
  geom_vline(aes(xintercept = lloq), linetype = "dashed", color = "red") +
  geom_vline(aes(xintercept = uloq), linetype = "dashed", color = "red") +
  facet_wrap(~ metabolite, scales = "free_x") +
  cowplot::theme_cowplot()
```

Let's remake this plot, taking out all metabolites that have all missing values.

```{r}
water_nomiss <- water %>%
  group_by(metabolite) %>%
  mutate(non_missing = if_else(is.na(value) == FALSE, 1, 0),
         total_non_missing = sum(non_missing)) %>%
  filter(total_non_missing > 0)

water_nomiss %>%
  ggplot(aes(x = value)) +
  geom_histogram(bins = 100) +
  geom_vline(aes(xintercept = lloq), linetype = "dashed", color = "red") +
  geom_vline(aes(xintercept = uloq), linetype = "dashed", color = "red") +
  facet_wrap(~ metabolite, scales = "free_x") +
  cowplot::theme_cowplot()
```

One challenge is that imputing values very close to 0 can be difficult. Let's try to assess how wide the distribution is relative to this small range near 0. To do this, let's divide the inter quartile range of each metabolite by its lloq.
```{r, fig.height = 5}
water_nomiss %>%
  mutate(iqr_value = IQR(value, na.rm = TRUE)) %>%
  slice(1) %>%
  mutate(iqr_over_lloq = iqr_value / lloq) %>%
  ggplot(aes(x = iqr_over_lloq, y = factor(metabolite) %>% fct_reorder(iqr_over_lloq))) +
  geom_point(aes(color = total_non_missing)) +
  labs(
    x = "IQR / lloq",
    y = "Metabolite",
    title = "Dot plot of range of 50% of values relative to the lloq\n(range to be imputed)"
  )
```

This plot shows that, at least as far as sampling the unknown values is concerned, Pseudoephedrine, Tramadol, Benzoylecgonine, Phentermine, Amphetamine, MDMA, Tapentadol, and Cocaine will be the easiest to estimate. MDMA and Tapentadol have a lot of missing values, so they will be difficult to impute as well. Overall, however, the distributions of observed values are very close to the lloq, so we cannot ignore the information about the observed values when trying to generate the unobserved values below the lloq.

## Relationships among metabolites
Let's look at only the most common metabolites. We will only take those that have at least 50 of the 99 possible observations.

```{r, message=F, fig.width=20, fig.height=20}
water_nomiss %>%
  filter(total_non_missing >= 50) %>%
  select(metabolite, value, location, time_pretty, machine, extraction) %>%
  spread(metabolite, value) %>%
  select(5:14) %>%
  mutate_all(~log(.)) %>%
  ggscatmat(corMethod = "spearman")
```

There doesn't seem to be a monstrous amount of structure here. Benzoylecgonine and Cocaine are obviously correlated. This graph may need some more careful study from Chris, who has more pharmacy training.