---
title: "UF Waste Water Analysis"
author: "Dominick Lemas"
date: "7/20/2019"
output: 
  html_document:
    theme: spacelab 
    highlight: tango
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(Hmisc)

# # Read data: Matt
# water <- read_tsv("../data/water_cleaned.txt") %>% mutate_if(is.character, funs(na_if(., "")))

load("../data/water.RData")
water=water.df

```


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# counts of all metabolites across all samples/sites
drugs=water %>%
  select(metabolite_name, barcode, time, run, location, value) %>%
  mutate(tmp=ifelse(value=="NA",0,1)) %>%
  group_by(metabolite_name) %>%
  tally(tmp) %>%
  rename(value=n) %>%
  filter(value >0) 

data=drugs %>% arrange(value)

# counts of metabolites within site
drug_location=water %>%
  select(metabolite_name, time, location, value) %>%
  mutate(tmp=ifelse(value=="NA","NA",1)) %>%
  group_by(metabolite_name, location) %>%
  tally(tmp) %>%
  rename(value=n) %>%
  filter(value>0) %>% 
  mutate(present=ifelse(value>0, TRUE, FALSE)) %>%
  select(metabolite_name,location,present) %>%
  spread(location,present) %>%
  mutate(species_new = case_when(is.na(`1`) ~ "FALSE",
                          is.na(`1`) ~ "TRUE")

         # start here

```

# Overview
Wastewater samples were manually collected  during the football game between Florida and Kentucky on Saturday, September 8, 2018 (n = 80,651). Samples were collected near the Ben Hill Griffith Stadium at three discrete locations. Samples were collected at each site every 30 minutes beginning approximately an hour before kickoff until 30 minutes after the game.

### All Samples

Variables | Value
------------- | -------------
Total # of observations | `r sum(drugs$value)`
Total # of locations | `r length(unique(water$location))`
Total # of time points | `r length(unique(water$time))`
Total # of metabolites | `r length(unique(water$metabolite_name ))`
Total # of runs | `r length(unique(water$run))`



```{r message=FALSE, warning=FALSE, echo=FALSE, fig.cap = "Figure 1: Metabolites detected in all samples."}

# Reorder
data %>%
  mutate(percent=(value/66)*100) %>%
  arrange(value) %>%
  mutate(metabolite_name=factor(metabolite_name,metabolite_name)) %>%
  ggplot( aes(x=metabolite_name, y=percent)) +
    geom_segment( aes(x=metabolite_name, xend=metabolite_name, y=0, yend=percent), color="skyblue", size=1) +
    geom_point( color="blue", size=4, alpha=0.6) +
    theme_light() +
    coord_flip() +
    theme(
      panel.grid.major.y = element_blank(),
      panel.border = element_blank(),
      axis.ticks.y = element_blank()
    ) + xlab("") + ylab("Percentage of Samples")
```


```{r,message=FALSE, warning=FALSE, echo=FALSE}

# observation by location: yes/no 
loc=water %>%
  select(metabolite_name,time, run, location, value) %>%
  mutate(tmp=ifelse(value=="NA",0,1)) %>%
  filter(tmp==1 & run==2) %>%
  spread(location, tmp)

# observation by location: yes/no 
# needs to be true/false across all times
loc=water %>%
  select(metabolite_name,time, run, location, value) %>%
  mutate(tmp=ifelse(value=="NA",0,1)) %>%
  filter(tmp==1 & run==2) %>%
  spread(location, tmp)

```

### Samples by location

Variables | Value
------------- | -------------
Location 1 # of obs  | `r location$count[1]`
Location 2 # of obs  | `r location$count[2]`
Location 3 # of obs  | `r location$count[3]`


```{r message=FALSE, warning=FALSE, echo=FALSE, fig.cap = "Figure 1: Metabolites detected in all samples."}

g <- ggplot(time, aes(x = time, y = count, color=location))+geom_bar(stat="identity")+theme_minimal()
g

```
