---
title: "How to simulate data for Amanda MS thesis"
author: "Matthew Shane Loop, PhD"
date: "`r Sys.Date()`"
output: html_document
---

```{r, warning=F, message = F}
library(tidyverse)
library(truncnorm)
```


Our goal is to create a dataset that looks quite similar to the observed tramadol data for this project. However, we will then create modifications to the dataset that will help us evaluate different possible conditions that others may see in their own datasets. These conditions that we will vary are:

1. lower limit of detection cutoff, meant to induce varying degrees of missing data
2. type of imputation method used (kNN, random forest, or a fully Bayesian model with Tobit regression)

The mean and standard deviation for the *observed* tramadol data are:
```{r}
water <- read_tsv("../data/water_cleaned.txt")
water %>%
  filter(metabolite == "Tramadol", is.na(value) == FALSE) %>%
  summarise(
    mean = mean(value),
    std_dev = sd(value)
  )
```


Therefore, we will detail below how to generate the data. The steps are:

1. Generate 10 random effects from a $N(0, \sigma^2 = 2)$, as a proxy for "time of collection". These random effects will be kept constant throughout all iterations of the simulation.
2. Generate 3 random effects from $N(0, \sigma^2 = 2)$, as a proxy for "location of collection". These random effects will be kept constant throughout all iterations of the simulation.
3. Generate $n=60$ observations for each of the 30 groups (10 times and 3 locations) from a truncated normal distribution: $y_{ijk} \sim \textrm{truncN}(\mu = 2.5 + u_i + v_j, \sigma = 3.5, a = 0, b = \inf)$
    * The generated distribution will *not* have a mean of $2.5 + u_i + v_j$, but a more complicated formula for the mean based on the [truncated normal distribution](https://en.wikipedia.org/wiki/Truncated_normal_distribution). 
    * So I guess the intercept will *not* be 2.5. But will it be the mean of a truncated normal which was *generated* from a mean 2.5 with $a = 0$, on average? Do we still not need to think about the random effects? If not, then the mean would be `etruncnorm(mean = 2.5, sd = 3.5 + 1 + 1, a = 0, b = Inf)` = `r round(etruncnorm(mean = 2.5, sd = 3.5 + 1 + 1, a = 0, b = Inf), digits = 2)`.
        * A previous version of this calculation used 11.5 as the standard deviation. In those cases, I got a mean of around 12 or 13, which is what Amanda was getting in her simulations for the intercept. That makes complete sense. The data we are generating *doesn't* have a mean of 2.5, since it's generating a truncated normal.
4. For the given proportion of missing that you want to achieve (e.g., proportion of 0.1 missing), calculate the quantile of the *marginal* generated truncated normal distribution that corresponds to that proportion
    * `qtruncnorm(mean = 2.5, sd = 3.5 + 1 + 1, a = 0, b = Inf, p = 0.1)` = `r round(qtruncnorm(mean = 2.5, sd = 3.5 + 1 + 1, a = 0, b = Inf, p = 0.1), digits = 2)`
5. If a value of $y_{ijk}$ is less than this value, then set it to missing
6. Repeat steps 3 - 5 1,000 times for the given simulation condition.

For each simulation condition (i.e., proportion of data that is missing), you should repeat steps 3 - 6.
        
# Example of creating sim

```{r}
set.seed(2343)
sim_data = expand.grid(
  u = rnorm(10, 0, sd = 1),
  v = rnorm(3, 0, sd = 1),
  prop_missing = seq(0.1, 0.5, 0.1),
  iteration = seq(1, 1000, 1)
) %>%
  as_tibble() %>%
  group_by(prop_missing, iteration) %>%
  nest() %>%
  rename(random_effects = data) %>%
  mutate(
    data = map2(prop_missing, random_effects, ~tibble(u = rep(.y$u, 60), v = rep(.y$v, 60), id = seq(1, 1800, 1)) %>%
                  group_by(u, v) %>%
                  mutate(
                    y = rtruncnorm(n = 1, a = 0, b = Inf, mean = 2.5 + u + v, sd = 3.5)
                  ))
  ) %>%
  select(-random_effects)
```

Check the mean and sd of `y` in each dataset:
```{r}
sim_data %>%
  unnest(data) %>%
  ungroup() %>%
  group_by(prop_missing, iteration) %>%
  summarise(mean_y = mean(y),
            sd_y = sd(y)
  ) %>%
  ggplot(aes(x = mean_y)) +
  geom_histogram() +
  facet_wrap(~prop_missing)
```

* So, we expected the mean to be `r round(etruncnorm(mean = 2.5, sd = 3.5 + 1 + 1, a = 0, b = Inf), digits = 2)`, but the mean looks to be about 4.15. What are we missing?
* What's the sample estimate of the mean of the random effects for one of these datasets?
    * `r sim_data$data[[1]] %>% ungroup() %>%  summarise(mean_u = mean(u), mean_v = mean(v))`
    * So what's the expected value for that? `r round(etruncnorm(mean = 2.5 - 1.73 -0.749, sd = 3.5 + 1 + 1, a = 0, b = Inf), digits = 2)` A bit closer.
